### 2018-05-24 5_eval.tex
Write some words on limitations.

%As a simple example of the compilation process discussed in Section~\ref{ch:impl:proc:x-compiler:compilation}, 
Consider two tiny meaningless function represented in Figure~\ref{ex:test-both-code} (in the C language on the left-hand side, the \porthos[1] input language on the right-hand side).
The functions are state-equivalent (represent the same state machine) and contain three nested \texttt{while}-loops.
On the example of these functions we will show the differences in compilation and loop unrolling stages between \porthos[1] and \porthos[2].
%contains several syntactic elements (such as prefix increment and loop-breaking statements), which are supported by \porthos[2] comparing to its predecessor.
%In the Figure, the control-flow subgraph \xgraph[CF] of the non-unrolled event-flow graph is presented on the right-hand side (

\begin{figure}[!h]
\begin{minipage}{.53\textwidth}
\begin{lstlisting}[language=Java,basicstyle=\ttfamily\small]
void t0(int& x) {
     int a = 1, c = 1;
     while (a == 1) {
         int b = 1;
         while (b == 1) {
             while (c == 1) {
                 x = c;
             }
             x = b;
         }
     }
     x = a;
 }
\end{lstlisting}
\end{minipage}
%
\begin{minipage}{.45\textwidth}
\begin{lstlisting}[language=Java,basicstyle=\ttfamily\small]
{ x }
thread t0 {
     a <- 1;
     c <- 1;
     while (a == 1) {
         b <- 1;
         while (b == 1) {
             while (c == 1) {
                 x := c
             };
             x := b
         };
     };
     x := a
 }
\end{lstlisting}
\end{minipage}
\caption{Example: A demonstrative cyclic function}
\label{ex:test-both-code}
\end{figure}

@@

The Figure~\ref{ex:test-both-pic} illustrates the data structure which the functions in Figure~\ref{ex:test-both-code} are compiled to.
The left-hand side picture represents the non-unrolled \xgraph[CF] generated by \porthos[2], and the right-hand picture represents the AST generated by \porthos[1].

@@

\begin{figure}[!h]
%
\begin{minipage}{.49\textwidth}
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/PorthosC/t0.png}
\end{minipage}
%
\begin{minipage}{.49\textwidth}
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/Porthos/t0.png}
\end{minipage}
%
\caption{The control-flow graphs of the functions presented in Figure~\ref{ex:test-both-code}}
\label{ex:test-both-pic}
\end{figure}

Two compiled the graphs are equivalent up to the extra \texttt{nop}-events in the \porthos[2] graph, which are necessary for correct encoding as it was discussed in Section~\ref{ch:enc:bmc:cf}.
However, the unrolled graphs presented in Figure~\ref{ex:test-both-pic-unroll} look differently as \porthos[2] uses different unrolling algorithm.
The labels of events in the left-hand side picture (produced by \porthos[2]) are augmented by the unrolling depth number, which is separated from the event label by comma.

@@

\begin{figure}[!h]
%
\begin{minipage}{.6\textwidth}
  \includegraphics[height=.6\textheight,width=\textwidth]{img/my/graphs/unrolling-comparison/PorthosC/t0_unrolled.png}
\end{minipage}
%
\begin{minipage}{.39\textwidth}
  \includegraphics[height=\textheight,width=\textwidth]{img/my/graphs/unrolling-comparison/Porthos/t0_unrolled.png}
\end{minipage}
%
\caption{The unrolled control-flow graphs of the functions presented in Figure~\ref{ex:test-both-code}}
\label{ex:test-both-pic-unroll}
\end{figure}

>>>>

%As a simple example of the compilation process discussed in Section~\ref{ch:impl:proc:x-compiler:compilation}, 
Consider two tiny equivalent functions in C (left) and the \porthos[1] input language (right) represented in Figure~\ref{ex:both-cf}. %(in the C language on the left-hand side, the \porthos[1] input language on the right-hand side).
%The functions are state-equivalent (represent the same state machine) and 
The functions does not compute any useful value, however they contain three nested \texttt{while}-loops and thus can serve as an illustration of the differences in the program compilation and unrolling between \porthos[1] and \porthos[2].
%contains several syntactic elements (such as prefix increment and loop-breaking statements), which are supported by \porthos[2] comparing to its predecessor.
%In the Figure, the control-flow subgraph \xgraph[CF] of the non-unrolled event-flow graph is presented on the right-hand side (

\begin{figure}[!h]
%\begin{minipage}{.53\textwidth}
\begin{subfigure}[b]{.53\textwidth}\centering
\begin{lstlisting}[language=Java,basicstyle=\ttfamily\small]

void t0(int &x) {
     int a = 1;
     int c = 1;
     while (a == 1) {
         int b = 1;
         while (b == 1) {
             while (c == 1) {
                 x = c;
             }
             x = b;
         }
     }
     x = a;
 }

\end{lstlisting}
\caption{An example in the C language}
\label{ex:both-cf:ptsC}
\end{subfigure}
%\begin{minipage}{.45\textwidth}
\begin{subfigure}[b]{.45\textwidth}\centering
\begin{lstlisting}[language=Java,basicstyle=\ttfamily\small]
{ x }
thread t0 {
     a <- 1;
     c <- 1;
     while (a == 1) {
         b <- 1;
         while (b == 1) {
             while (c == 1) {
                 x := c
             };
             x := b
         };
     };
     x := a
 }
\end{lstlisting}
\caption{An example in the \porthos[1] input language}
\label{ex:both-cf:pts1}
\end{subfigure}
\caption{Example: A demonstrative cyclic function}
\label{ex:both-cf}
\end{figure}

@@

The Figure~\ref{ex:test-botrepresentedh-pic} illustrates the data structure which the functions in Figure~\ref{ex:test-both-code} are compiled to.
The left-hand side picture represents the non-unrolled \xgraph[CF] generated by \porthos[2], and the right-hand picture represents the AST generated by \porthos[1].

@@

\begin{figure}[!h]
%
\begin{subfigure}[t]{.49\textwidth}\centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/PorthosC/t0.png}
  \hfill
  \caption{The compiled \xgraph{} of the function in Figure~\ref{ex:both-cf:ptsC}}
  \label{ex:both-cf:graph:ptsC}
\end{subfigure}
%
\begin{subfigure}[t]{.49\textwidth}\centering
  \includegraphics[width=\textwidth,keepaspectratio]{img/my/graphs/unrolling-comparison/Porthos/t0.png}
  \hfill
  \caption{The compiled AST of the function in Figure~\ref{ex:both-cf:pts1}}
  \label{ex:both-cf:graph:pts1}
\end{subfigure}
%
\caption{The control-flow graphs of the functions represented in Figure~\ref{ex:both-cf}}
\label{ex:test-both-pic}
\end{figure}

Two compiled the graphs are equivalent up to the extra \texttt{nop}-events in the \porthos[2] graph, that are necessary for correct encoding as it was discussed in Section~\ref{ch:enc:bmc:cf}, and \texttt{skip}-events in \porthos[1] graph.
However, the unrolled graphs presented in Figure~\ref{ex:test-both-pic-unroll} are different as \porthos[2] uses different unrolling algorithm.
The labels of events in the left-hand side picture (produced by \porthos[2]) are augmented by the unrolling depth number, which is separated from the event label by comma.

@@

\begin{figure}[!h]
%
\begin{subfigure}[b]{.6\textwidth}\centering
  \includegraphics[height=.6\textheight,width=\textwidth]{img/my/graphs/unrolling-comparison/PorthosC/t0_unrolled.png}
  \hfill
  \caption{The unrolled \xgraph{} of the function in Figure~\ref{ex:both-cf:ptsC}}
  \label{ex:both-cf:graphU:ptsC}
\end{subfigure}
\hfill
%
\begin{subfigure}[b]{.3\textwidth}\centering
  \includegraphics[height=.9\textheight,width=\textwidth]{img/my/graphs/unrolling-comparison/Porthos/t0_unrolled.png}
    \caption{The unrolled AST of the function in Figure~\ref{ex:both-cf:pts1}}
    \hfill
  \label{ex:both-cf:graphU:pts1}
\end{subfigure}
\hfill
%
\caption{The unrolled control-flow graphs of the functions represented in Figure~\ref{ex:test-both-code}}
\label{ex:test-both-pic-unroll}
\end{figure}

### 2018-05-24 99_summary.tex
Write some words on limitations.

  \item For ease the process of adding support for new domain-specific functions (for example, the Kernel-specific atomic write function \texttt{atomic\_store}), we implemented the \textit{invocation hooking mechanism}, which allows to modify the compilation process without changing the interpreter.
  The invocation hooks serve as a knowledge base for the program domain, that are to be extended in future.
  We illustrate this mechanism with the basic support for Linux kernel litmus tests.

@@

- improve the encoding: an abstraction over Z

@@

- hooks : flexible. but still in Java, not as separate module (as it requires turing-complete language to be expressive enough) => extension of the knowledge base for supporting new platforms / languages

@@

- testing with new solvers

>>>>

  \item For ease the process of adding support for new domain-specific functions (for example, the Kernel-specific atomic write function \texttt{atomic\_store}), we implemented the \textit{invocation hooking}, a flexible mechanism for intercepting the compilation process without changing the interpreter.
  The invocation hooking mechanism serves as a knowledge base for the program domain, that is to be filled and extended in future.
  Invocation hooks are defined in Java and thus are flexible, though their extension and modification requires some knowledge of the internals of the tool.
  We illustrate this mechanism with the basic support for Linux kernel litmus tests.

@@

Current implementation of \porthos[2] has the following limitations, that might define the direction of the future work.

\begin{itemize}
\item The major flaw of \porthos[2] as a tool that performs the complete software analysis is the its sensitivity to the combinatorial explosion.
%TODO: show it in table , reference here the table
As it was shown in Section~\ref{ch:eval:perf}, the number of events generated by the program grow rapidly as the user increases the unrolling bound.
One possible way to reduce the number of states of the program might be applying some traditional techniques for fighting the state explosion problem (such as concrete execution as a part of concolic execution~\cite{majumdar2007hybrid}), however this must be done \textit{with considering the weak memory model}, because otherwise it could possibly lead to the loss of states.
% cannot be applied to our problem \textit{before} the weak memory model is considered, 
%One possible enhancement, that could treat but not cure this flaw, could be an extra analysis stage carried before the unrolling, that analyses

%\item As its predecessor, \porthos[2] does not propose any heuristic for finding the optimal unrolling bound.

\item As its predecessor, \porthos[2]

\end{itemize}

%- improve the encoding: an abstraction over Z
- testing with new solvers

@@

%- hooks : flexible. but still in Java, not as separate module (as it requires turing-complete language to be expressive enough) => extension of the knowledge base for supporting new platforms / languages

@@
